### 2012-01-30 docs/notes.tex
Small edits to notes.

It is straightforward extend this to marked point processes where each event contains additional information.  In the context of relational events occurring among $N$ nodes, for example, we let the \emph{risk set} $\mathcal{R}$ of possible events include all allowed dyads.  Let each dyad $(i,j) \in \mathcal{R}$ have an intensity function $\lambda_{ij}(t|\cdot)$ that is piecewise constant.  As shown in Figure \ref{fig:example}, we assume each intensity function $\lambda_{ij}(t)$ may only change following an event involving either $i$ or $j$.  Let $\tau_{i,j,m}$ be the time that $\lambda_{i,j}$ changed before the $m$th event and let $\mathcal{R}_{i,j}$ be the set of dyads involving either $i$ or $j$.  % Letting $ \mathcal{R}_{k_1,k_2}$ be the set of events that can occur from $k_1$ to $k_2$ and  $\boldsymbol{\tau}_{i,j}$ is the set of knots where the respective intensities may change, we may write the likelihood as follows:
% \begin{align}
% \mathcal{L}(\mathcal{A}|\theta) %&= \prod_{m=1}^M \lambda_{i_m,j_m}(t_m|\cdot) \prod_{(i,j) \in \mathcal{R}} \prod_{k=1}^{|\boldsymbol{\tau}_{ij}|} \exp\{ - (\tau_{i,j,k} - \tau_{i,j,k-1}) \lambda_{ij}(\tau_{i,j,k} | \cdot) \} \\
% &= \prod_{m=1}^M \lambda_{i_m,j_m}(t_m|\cdot) \prod_{k_1=1}^K \prod_{k_2=1}^K \prod_{(i,j) \in \mathcal{R}_{k_1,k_2}} \prod_{r=1}^{|\boldsymbol{\tau}_{i,j}|} \exp\{ - (\tau_{k_1,k_2,r} - \tau_{k_1,k_2,r-1}) \lambda_{ij}(\tau_{i,j,r} | \cdot) \} 
% \end{align}
% \begin{align}
% \mathcal{L}(\mathcal{A}|\theta) &= \prod_{m=1}^M \lambda_{i_m,j_m}(t_m|\cdot) \prod_{r=1}^N \exp\{ - (t_m - \tau_{i,r,m}) \lambda_{ir}(t_m | z_i,z_r)  - (t_m - \tau_{r,j,m}) \lambda_{rj}(t_m | z_r,z_j) \} 
% \end{align}
\begin{align}
\mathcal{L}(\mathcal{A}|\theta) &= \prod_{m=1}^M \lambda_{i_m,j_m}(t_m|\cdot) \prod_{(i,j) \in \mathcal{R}_{i_m,j_m}}\exp\{ - (t_m - \tau_{i,j,m}) \lambda_{ij}(t_m | z_i,z_j) \}
\end{align}

@@

@@

\bibliographystyle{plain}
\bibliography{refs}

>>>>

It is straightforward extend this to marked point processes where each event contains additional information.  In the context of relational events occurring among $N$ nodes, for example, we let the \emph{risk set} $\mathcal{R}$ of possible events include all allowed dyads.  Let each dyad $(i,j) \in \mathcal{R}$ have an intensity function $\lambda_{ij}(t|\cdot)$ that is piecewise constant.  As shown in Figure \ref{fig:example}, we assume each intensity function $\lambda_{ij}(t)$ may only change following an event involving either $i$ or $j$.  Let $\tau_{i,j,m}$ be the time that $\lambda_{i,j}$ changed before the $m$th event and let $\mathcal{R}_{i,j}$ be the set of dyads involving either $i$ or $j$.  [TODO: We further assume that all intensity functions change at times $t=0$ and $t=t_M$.  Also, assume the first event is drawn uniformly from the risk set.]
% Letting $ \mathcal{R}_{k_1,k_2}$ be the set of events that can occur from $k_1$ to $k_2$ and  $\boldsymbol{\tau}_{i,j}$ is the set of knots where the respective intensities may change, we may write the likelihood as follows:
% \begin{align}
% \mathcal{L}(\mathcal{A}|\theta) %&= \prod_{m=1}^M \lambda_{i_m,j_m}(t_m|\cdot) \prod_{(i,j) \in \mathcal{R}} \prod_{k=1}^{|\boldsymbol{\tau}_{ij}|} \exp\{ - (\tau_{i,j,k} - \tau_{i,j,k-1}) \lambda_{ij}(\tau_{i,j,k} | \cdot) \} \\
% &= \prod_{m=1}^M \lambda_{i_m,j_m}(t_m|\cdot) \prod_{k_1=1}^K \prod_{k_2=1}^K \prod_{(i,j) \in \mathcal{R}_{k_1,k_2}} \prod_{r=1}^{|\boldsymbol{\tau}_{i,j}|} \exp\{ - (\tau_{k_1,k_2,r} - \tau_{k_1,k_2,r-1}) \lambda_{ij}(\tau_{i,j,r} | \cdot) \} 
% \end{align}
% \begin{align}
% \mathcal{L}(\mathcal{A}|\theta) &= \prod_{m=1}^M \lambda_{i_m,j_m}(t_m|\cdot) \prod_{r=1}^N \exp\{ - (t_m - \tau_{i,r,m}) \lambda_{ir}(t_m | z_i,z_r)  - (t_m - \tau_{r,j,m}) \lambda_{rj}(t_m | z_r,z_j) \} 
% \end{align}
\begin{align}
\mathcal{L}(\mathcal{A}|\theta) &= \prod_{m=1}^M \lambda_{i_m,j_m}(t_m|\cdot) \prod_{(i,j) \in \mathcal{R}_{i_m,j_m}}\exp\{ - (t_m - \tau_{i,j,m}) \lambda_{ij}(t_m | z_i,z_j) \}
\end{align}

@@

Another idea: $\log \lambda_{ij} = (\pi_i \cdot \pi_j) \eta s(t,i,j)$

@@

I do not believe it is possible to perform EM for a model where we have the more general linear predictor for the intensity function.  Since the assignment of one node depends on the assignments of the other nodes, we suffer combinatorial explosion.
\bibliographystyle{plain}
\bibliography{refs}
